---
title: "individual2"
author: "Dana Thacker"
date: "2/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco) 

#Question 1 - How are the ratings distributed?
hist(choco$Rating)
boxplot(choco$Rating)
#The histogram is unimodal and normal barring the outliers to the left of the main portion of data. If the outliers are taken into account, the histogram is left skewed, and still unimodal. The boxplot clearly shows the outliers underneath the main portion of the plot and the variance of the boxplot looks relatively small.



#Question 2 - How does the number of ratings depend on the location of the company?
counts <- table(choco$Location)
barplot(counts, main='Company Ratings', xlab ='Company')

sCC <- sort(counts)
sCC

ratingVct <- (choco$Rating)
ratingMean <- mean(ratingVct, na.rm=TRUE)
ratingMean
#The average rating is 3.184

USAdata <- choco[choco$Location == "U.S.A.", ]
USARating <- (USAdata$Rating)
USARatingMean <- mean(USARating, na.rm=TRUE)
USARatingMean
#The average USA rating is 3.171

Francedata <- choco[choco$Location == "France", ]
FranceRating <- (Francedata$Rating)
FranceRatingMean <- mean(FranceRating, na.rm=TRUE)
FranceRatingMean
#The average France rating is 3.25

Canadadata <- choco[choco$Location == "Canada", ]
CanadaRating <- (Canadadata$Rating)
CanadaRatingMean <- mean(CanadaRating, na.rm=TRUE)
CanadaRatingMean
#The average Canada rating is 3.301

UKdata <- choco[choco$Location == "U.K.", ]
UKRating <- (UKdata$Rating)
UKRatingMean <- mean(UKRating, na.rm=TRUE)
UKRatingMean
#The average U.K. rating is 3.063

Spaindata <- choco[choco$Location == "Spain", ]
SpainRating <- (Spaindata$Rating)
SpainRatingMean <- mean(SpainRating, na.rm=TRUE)
SpainRatingMean
#The average Spain rating is 3.264

Japandata <- choco[choco$Location == "Japan", ]
JapanRating <- (Japandata$Rating)
JapanRatingMean <- mean(JapanRating, na.rm=TRUE)
JapanRatingMean
#The average Japan rating is 3.129

#After comparing the means from various countries in which chocolate was added to the dataset, there appear to be no major differences in the location of the country and the average rating of the chocolate. Of the countries that have more chocolates in the dataset, Canada ranks the highest in average chocolate ratings of 3.301 and the U.K. ranks the lowest at 3.063. These average rankings do not show a drastic correlation between the average rating of the chocolate and the location of the company.


#Question 3 - Do ratings depend on the cocoa percentage of a chocolate bar?
plot(choco$Rating, choco$Cocoa_Percent)

counts2 <- table(choco$Rating, choco$Cocoa_Percent)
barplot(counts2)

data = choco[,c("Cocoa_Percent", "Rating")]

lowCocoa = data[data$Cocoa_Percent < 85, ]
lowCocoaMean <- mean(lowCocoa$Rating)
lowCocoaMean
#Low Cocoa Percentage mean rating of 3.199

highCocoa = data[data$Cocoa_Percent >= 85, ]
highCocoaMean <- mean(highCocoa$Rating)
highCocoaMean
#Low Cocoa Percentage mean rating of 2.8

plot(lowCocoa, highCocoa)

#It appears as though the cocoa percentage of a chocolate bar does impact the rating of the chocolate. Chocolate with lower than 85% cocoa has an average ranking of 0.4 higher than chocolate with higher than 85% cocoa.

#Question 4 - How do different bean origins compare in terms of the flavor of chocolates?
originCount <- table(choco$Bean_Origin)
sOC <- sort(originCount)
sOC

data2 = choco[,c("Bean_Origin", "Rating")]

venDta <- choco[choco$Bean_Origin == "Venezuela", ]
venRate <- (venDta$Rating)
venMeanRate <- mean(venRate, na.rm=TRUE)
venMeanRate
#Venezuela Mean Rating 3.224

peruDta <- choco[choco$Bean_Origin == "Peru", ]
peruRate <- (peruDta$Rating)
peruMeanRate <- mean(peruRate, na.rm=TRUE)
peruMeanRate
#Peru Mean Rating 3.165

ecuDta <- choco[choco$Bean_Origin == "Ecuador", ]
ecuRate <- (ecuDta$Rating)
ecuMeanRate <- mean(ecuRate, na.rm=TRUE)
ecuMeanRate
#Ecuador Mean Rating 3.159

USAdata2 <- choco[choco$Bean_Origin== "U.S.A.", ]
USARating2 <- (USAdata2$Rating)
USARatingMean2 <- mean(USARating2, na.rm=TRUE)
USARatingMean2
#USA Mean Rating 3.217

VietnamDTA <- choco[choco$Bean_Origin== "Vietnam", ]
vietRate <- (VietnamDTA$Rating)
vietMeanRate <- mean(vietRate, na.rm=TRUE)
vietMeanRate
#Vietnam Mean Rating 3.254

philiDta <- choco[choco$Bean_Origin == "Philippines", ]
philiRate <- (philiDta$Rating)
philiMeanRate <- mean(philiRate, na.rm=TRUE)
philiMeanRate
#Philippines Mean Rating 3.105

indiaDta <- choco[choco$Bean_Origin == "India", ]
indiaRate <- (indiaDta$Rating)
indiaMeanRate <- mean(indiaRate, na.rm=TRUE)
indiaMeanRate
#India Mean Rating 3.155hwyMPG <- mpg$hwy


meanRates <- c(venMeanRate, peruMeanRate, ecuMeanRate, USARatingMean2, vietMeanRate, philiMeanRate, indiaMeanRate)
meanRates

barplot(meanRates)

#Based on the analysis I have done from comparing mean ratings of several bean origins, it appears that there are no large differences in the average means of the countries. There are slight variations, but they are all within 0.1 of each others ratings. The average mean of all of the ratings is also very close to all of these average ratings. This leads me to believe that the origin of the beans have no real effect on the rating of the chocolate.


#Question 5- Most desirable characteristics as determined by rating

data3 = choco[,c("Characteristics1", "Rating")]
    newdata = aggregate(x = data3$Rating, by = list(data3$Characteristics1), FUN = mean)
    newdata = tail(newdata[order(newdata$x),],5)
    newdata
    newdata = as.matrix(newdata)

#Some of the top characteristics that contributed to the higher ratings of chocolate were "pronounced berry," "simple red berry," "smoth," "sweet spice," and "well defined." All of these characteristics resulted in a rating of 4 which is quite high as compared to the average chocolate rating.

```

**North America**
U.S.A.
Mexico
St. Vincent-Grenadines
Tobago
Trinidad
El Salvador
Puerto Rico
Panama
St. Lucia
Congo
Cuba
Grenada
Honduras
Jamaica
Haiti
Costa Rica
Guatemala
Belize
Nicaragua
Dominican Republic

**South America**
Brazil
Ecuador
Peru
Venezuela
Bolivia
Suriname
Colombia
Bolivia

**Africa**
Uganda
Madagascar
DR Congo
Gabon
Principe
Sao Tome & Principe
Cameroon
Liberia
Nigeria
Sierra Leone
Togo
Ivory Coast
Sao Tome
Ghana
Tanzania

**Asia**
Philippines
India
Burma
Sulawesi
Sumatra
Sri Lanka
Taiwan
Thailand
Malaysia
Indonesia
Vietnam

**Australia**
Australia

**Europe**
Martinique

**Oceania**
Samoa
Solomon Islands
Vanuatu
Fiji
Papua New Guinea

Blend x2