---
title: 'hw2.Rmd'
author: "Andrew Fahmy"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
    choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv")
    str(choco)
```

# 1.
```{r}
    boxplot(choco$Rating)
    hist(choco$Rating)
```

The ratings are mostly between 2.2 to 4.0. The average rating of all of the
chocolates is about 3.25. There are a few outliers but they are only at the
bottom of the scale, from around 1.0 to 2.0.

# 2.
```{r}
    tbl = tail(sort(table(choco$Location)), 5)
    tbl
    barplot(tbl)
```

The USA has way more than any other location. The USA as 800+ while other places
just reach 200 at most.

# 3.
```{r}
    data = choco[,c("Cocoa_Percent", "Rating")]
    d1 = data[data$Cocoa_Percent < 85, ]
    mean(d1$Rating)
    d2 = data[data$Cocoa_Percent >= 85, ]
    mean(d2$Rating)
    barplot(c(mean(d1$Rating), mean(d2$Rating)), col=c("red", "blue"))
```

I have divide data in chunks, with the red plot being the mean of ratings for
cocoa percent less than 85, and blue is mean of ratings for cocoa percent
greater then 85. It looks like they are close, but the lower cocoa percent
has a higher rating.

# 4.
```{r, fig.height = 5, fig.width =6}
    data = choco[,c("Bean_Origin", "Rating")]
    newdata = aggregate(x = data$Rating, by = list(data$Bean_Origin), FUN = mean)
    newdata = tail(newdata[order(newdata$x),],5)
    newdata
    newdata = as.matrix(newdata)
    barplot(newdata$x, names.arg = newdata$Group.1)

```


# 5.
```{r}
    data = choco[,c("Date", "Rating")]
    newdata = aggregate(x = data$Rating, by = list(data$Date), FUN = mean)
    plot(newdata)
    
```

This chart shows the relationship between the date and the ratings. In the
earlier years they had lower ratings and as time goes on you can see the
mean of the rating increase.