
---
title: 'team.Rmd'
author: "Andrew Fahmy, Dana Thacker"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
    choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv")
    # str(choco)
```



# 4.
```{r, fig.height = 5, fig.width =6}
    data = choco[,c("Bean_Origin", "Rating")]
    newdata = aggregate(x = data$Rating, by = list(data$Bean_Origin), FUN = mean)
    newdata = tail(newdata[order(newdata$x),],5)
    newdata
    newdata = as.matrix(newdata)
    #barplot(newdata$x, names.arg = newdata$Group.1)

```


# 5.
```{r}
    data = choco[,c("Date", "Rating")]
    newdata = aggregate(x = data$Rating, by = list(data$Date), FUN = mean)
    plot(newdata)
    
    
data3 = choco[,c("Characteristics1", "Rating")]
    newdata2 = aggregate(x = data3$Rating, by = list(data3$Characteristics1), FUN = mean)
    newdata2 = tail(newdata2[order(newdata2$x),],5)
    newdata2
    newdata2 = as.matrix(newdata2)



```

This chart shows the relationship between the date and the ratings. In the
earlier years they had lower ratings and as time goes on you can see the
mean of the rating increase.

Some of the top characteristics that contributed to the higher ratings of chocolate were "pronounced berry," "simple red berry," "smoth," "sweet spice," and "well defined." All of these characteristics resulted in a rating of 4 which is quite high as compared to the average chocolate rating.